Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

Concurrent program is a term used to describe multiple threads / processes running simultaneously to perform some computation. There are two different environments where concurrent programs are used: shared memory and distributed memory systems. Shared memory systems contain multiple processors / multi-core processors sharing a common memory and execute the computation through threads / processes. Thread communicate using shared memory and may use atomic instructions or traditional lock to execute some critical sections of the program. 
In shared memory environment, concurrent programmers use smart pointers to manually manage memory. Smart pointers are manual reference counting technique implemented by application programming interface. Distributed memory systems contain multiple processors with dedicated memory and processors are separated by some physical distance and connected via the network. In Distributed memory systems, processes on each processor and processes communicate by sending messages across the network to perform the computation. Both of the environment contain programs that run concurrently and requires some form of communication to perform desired computation. The distinction between both of the environments are communication technique used and memory. Both of the environments uses automatic memory management feature to help developers build applications with above-mentioned benefits.

>>>>

Concurrent program is a term used to describe multiple threads / processes running simultaneously to perform some computation. There are two different environments where concurrent programs are used: shared memory and distributed memory systems. Shared memory systems contain multiple processors / multi-core processors sharing a common memory and execute the computation through threads / processes. Threads communicate using shared memory and may use atomic instructions or traditional locks to execute some critical sections of the program. 
In a shared memory environment, concurrent programmers use smart pointers to manually manage memory. Smart pointers are a manual reference counting technique implemented by the application programming interface. Distributed memory systems contain multiple processors with dedicated memory and processors are separated by some physical distance and connected via a network. In distributed memory systems, processes execute on each processor and  communicate by sending messages across the network to perform the computation. Both of the environments contain programs that run concurrently and require some form of communication to perform the desired computation. The environments are distinguished by communcation technique and memory use. Both of the environments uses automatic memory management feature to help developers build applications with above-mentioned benefits.
